Bayesian Exploration in Deep Reinforcement Learning

### 2022-08-01 papers/CDRL/sample_paper.tex
TEMPORARY DEPLOY COMMIT

\begin{equation}
  v(\rvz) = \rvz + \rvu h(\rvw \rvz + b),
\end{equation}
\begin{equation}
  \left\lvert \det \frac{\partial v}{\partial \rvz} \right\rvert =
  \left\lvert 1 + \rvu^\top h^\prime(\rvw^\top \rvz + b) \rvw \right\rvert,
\end{equation}

@@

\begin{equation}
  Z_\theta(\rvx,a) = v_\theta^{-1}(z, \rvx^\prime)_a
\end{equation}
\begin{equation*}
  z \sim \N(0, I); \quad \rvx^\prime = h(\rvx)
\end{equation*}

>>>>

\begin{equation}
  v(\rvz) = \rvz + \rvu h(\rvw \rvz + b),
\end{equation}
\begin{equation}
  \det \left\lvert \frac{\partial v}{\partial \rvz} \right\rvert =
  \left\lvert 1 + \rvu^\top h^\prime(\rvw^\top \rvz + b) \rvw \right\rvert,
\end{equation}

@@

Similar to other DQN methods, we let \(Z_\theta(\rvx, a)\) be the \(a\)-th
element of a function \(\tilde{Z}_\theta : \R^{\lvert \X \rvert}
\rightarrow \R^{\lvert \A \rvert}\). This means that we need a conditional
normalizing flow \(v_\theta : \R^{\lvert \X \rvert} \times \R^{\lvert \A \rvert}
\rightarrow \R^{\lvert \A \rvert}\). Given that we have

\begin{equation}
  \T \tilde{Z}_\theta(\rvx)_a \defeq R(\rvx, a) + \max_{a^\prime \in \A}
  \tilde{Z}_\theta(\rvx^\prime)_{a^\prime}
\end{equation}

\noindent
we can see that any learning signal would only come for a single action. This
means that we need an elementwise flow so that we can learn each dimension
independently. Given elementwise conditional normalizing flow \(v_\theta\), we
define the loss function as

\begin{multline}
  \mathcal{L}_{\rvx, a}(\theta) \defeq \log p(v_\theta^{-1} (\rvx, v_{\tilde{
  \theta}} (\rvx^\prime, \vepsilon))_a; 0, 1) \\- \log
  \left\lvert \frac{\partial v^{-1}_{\theta}(\rvx, v_{\tilde{
  \theta}} (\rvx^\prime, \vepsilon))_a}{\partial v_{\tilde{
  \theta}} (\rvx^\prime, \vepsilon)_a} \right\rvert; \quad
  \vepsilon \sim \N(0, I_{\lvert \A \rvert})
\end{multline}

The most popular normalizing flows right now are buildt for large dimensional
spaces such as images. This includes coupling and autoregressive flows. Planar
flow is very easy to turn elementwise, but unfortunately does not have a closed
form inverse for most functions of \(h\). Although it does have one for
piecewise linear funcitons, those do not have second derivative, hence the
gradient of the log absolute determinant would be zero. This would mean it can
not learn appropriate transformations. Instead we define our own flow.

Equation~\ref{eq:luddeflow} shows the definitiona of the forward transformation
\(v_{w, b, c, d}\), with 4 free parameters \(w, b, c, d\). Unlike the planar
flow, this function is invertible and differentiable given any values for these
parameters. Equation~\ref{eq:luddeflow_inv} and
Equation~\ref{eq:luddeflow_inv_grad} show the closed form inverse and gradient
respectively.

% \begin{equation}
%   Z_\theta(\rvx,a) = v_\theta^{-1}(z, \rvx^\prime)_a
% \end{equation}
% \begin{equation*}
%   z \sim \N(0, I); \quad \rvx^\prime = h(\rvx)
% \end{equation*}

\begin{equation*}
  s(x) = \log(1 + \exp(x))
\end{equation*}
\begin{equation}
  v_{w, b, c, d}(z) = \sign(z + c) \left[ s(\lvert w(z + c) \rvert + b) 
  - s(b) \right] + d \label{eq:luddeflow}
\end{equation}

\begin{equation*}
  s^{-1}(x) = \log(\exp(x) - 1); \quad x > 0
\end{equation*}
\begin{equation}
  v^{-1}_{w, b, c, d}(z^\prime) = \frac{\sign(z^\prime - d)}{w}
  [ s^{-1}(\lvert z^\prime - d \rvert + s(b)) - b] - c \label{eq:luddeflow_inv}
\end{equation}

\begin{equation}
  \frac{\partial v^{-1}_{w,b,c,d}}{\partial z^\prime} = \frac{(e^b + 1)
  (z^\prime - d) e^{\lvert z^\prime - d \rvert} \sign{(x - d)}}{w \lvert
  z^\prime - d \rvert ((e^b + 1)e^{\lvert z^\prime - d \rvert} - 1)}
  \label{eq:luddeflow_inv_grad}
\end{equation}

Figure~\ref{fig:luddeflow} shows the effect of the free parameters. A simple
description is \(w\) changes the slope of the function, \(b\) changes the
\emph{linearity} of the function (as \(b\) goes to infinity, \(v\) approaches a
linear function), \(c\) shifts the horizontally, and \(d\) shifts the function
vertically.

\begin{figure}[ht]
  \vspace{.3in}
  % \centerline{\fbox{This figure intentionally left non-blank}}
  \includegraphics[width=\columnwidth]{luddeflow.png}
  \vspace{.3in}
  \caption{Illustration of the effect the free parameters have on the function).
  }\label{fig:luddeflow}
\end{figure}
